A Flux Scale for Southern Hemisphere 21cm EoR Experiments

### 2013-06-13 ms.tex
Edits of abstract and S1, along with some random stuff throughout.

%\title{The Reionization flux scale in the Southern Sky}
\title{A Flux Scale for Southern Hemisphere 21cm EoR Experiments}
\author{
Daniel C. Jacobs\altaffilmark{1},
Aaron R. Parsons\altaffilmark{2},
James E. Aguirre\altaffilmark{3},
Zaki Ali\altaffilmark{2},
Judd Bowman\altaffilmark{1},
Richard F. Bradley\altaffilmark{4,5,6},
Chris L.  Carilli\altaffilmark{7},
David R. DeBoer\altaffilmark{8},
Matthew R. Dexter\altaffilmark{8},
Nicole E. Gugliucci\altaffilmark{5},
Pat Klima\altaffilmark{5},
Dave H. E. MacMahon\altaffilmark{8}
Jason R. Manley\altaffilmark{9},
David F. Moore\altaffilmark{3},
Jonathan C. Pober\altaffilmark{2},
Irina I. Stefan\altaffilmark{10},
William P. Walbrugh\altaffilmark{9}}

@@

\begin{abstract}
We present a catalog of broad-band spectral measurements from the 
Donald C. Backer Precision Array for Probing
the Epoch of Reionization (PAPER) in South Africa observed in July and
September of 2011.  In order to reduce the impact of beam calibration, which proves to
be a difficult endeavor for transit telescopes such as PAPER, on the determination
of source spectra, we have focused on calibrating sources in a narrow declination range.
Since each source follows a nearly identical path through the primary beam, this
restriction allows beam calibration to be greatly reduced as a source of error,
yielding a dramatic improvement in the accuracy of source spectra measured in the 
100--200-MHz band which is receiving renewed attention by experiments seeking to
measure 21cm emission from the Epoch of Reionization (EoR). Using beam forming
and fringe-rate filtering we measure spectra for Pictor A, which provides a key flux reference for PAPER's EoR
power spectrum analysis, 
as well as \Nconf{} other sources at nearby declinations. Extrapolating from higher frequency
catalogs we set the flux scale in a Monte-Carlo fit across multiple sources. This fit 
propagates uncertainty from both catalog and measurement errors. Fitting new spectral 
models to both catalog and the new PAPER data we find a Pictor A flux model accurate to
1.4\%, confirming that Pictor A is a linear power law through the EoR band, and is an excellent calibrator. 
This accuracy is limited by the uncertainty in the catalog measurements we use
to estimate an absolute flux scale, and represents 
an order of magnitude improvement over previous measurements in this band.  
Comparing with prior measurements, 90\% are found to confirm and refine a power-law model for flux density.

\end{abstract}

@@

Numerous radio telescopes are now exploring the prospects for using
measurements of highly redshifted 21cm emission to inform our understanding of
cosmic reionization in the redshift range $6< z<12$, corresponding to radio
frequencies below 200 MHz (see reviews in
\citealt{Furlanetto:2006p2267,Morales:2010p8093,Pritchard:2012p9555}).  These
include telescopes aiming to measure the global temperature change of 21cm
emission during the Epoch of Reionization (EoR), such as the Compact
Reionization Experiment (CoRE), the Zero-spacing Interferometer \citep{Raghunathan:2011}  and the Experiment to Detect the Global EoR
Signature (EDGES; \citealt{Bowman:2010p8546}), and interferometers aiming to
measure the power spectrum of 21-cm EoR emission, such as the Giant Metre-wave
Radio Telescope (GMRT;
\citealt{Paciga:2011p9470,Paciga:2013p9627})\footnote{\url{http://gmrt.ncra.tifr.res.in/}},
the LOw Frequency ARray (LOFAR;
\citealt{Yatawatta:2013p9699})\footnote{\url{http://www.lofar.org/}}, the
Murchison Widefield Array (MWA;  \citealt{Bowman:2012p9138};
\citealt{Tingay:2013p9022}))\footnote{\url{http://www.mwatelescope.org/}}, and
the Donald C. Backer Precision Array for Probing the Epoch of Reionization
(PAPER; \citealt{Parsons:2010p6757,Pober:2013p9567})\footnote{\url{http://eor.berkeley.edu/}}.

As such, there has been a renewed interest in the spectral and spatial variation of
foreground emission in the 100--200 MHz frequency band that covers
the $z=6$--13 redshift range expected to encompass reionization
\citep{Furlanetto:2006p2267}.
In particular, the spectral properties of extra-galactic point-sources are important
both because they are valuable calibration references
and because they are strong foreground emitters that must be removed from 21-cm EoR measurements.
With the sparse availability of measured foreground properties in the
100--200-MHz frequency band over large areas of the sky \citep{deOliveiraCosta:2008p2242}, continued
foreground characterization is a
vital step en route to any 21-cm EoR detection.
At these low
frequencies the Southern sky is much less well known than the North, 
with catalog source fluxes at 150MHz being inaccurate at the 20\% level
for $\delta<-20$\arcdeg{} \citep{Slee:1995p7541,Vollmer:2005p6425}.
Both PAPER and the MWA are located in the southern hemisphere at radio-quiet
reserves being prepared for the upcoming Square Kilometer Array, and hence,
the
most extensive surveying work is now being conducted by the EoR experiments
themselves \citep{Jacobs:2011p8438,Williams:2012p8768,Bernardi:2013p9859}.

One significant complication to improving the state of affairs in foreground characterization
is that many 21cm EoR experiments, including LOFAR in the northern hemisphere, and
PAPER and MWA in the southern hemisphere, are designed for drift-scan observations or steered via phased array.
This design decision has largely been driven by the simplicity and cost-effectiveness of
phased and/or correlated dipoles to achieve the aggressive sensitivity requirements
for measuring the 21cm power spectrum of reionization.
%TODO ARP wanted a cite for the above.  I really don't know of a good one. Its it a bit of a broad statement
Adding to the challenge, these telescopes 
cover much wider fields of view ($>10$\arcdeg) and bandwidths
($\sim 100$\% fractional) than traditional dish telescopes.
Because they do not physically point, flux calibration for such arrays relies heavily
on an accurate model of the primary beam response to correct for an
the apparent flux scale that varies across the sky.
This direction dependent gain is currently uncertain to 10\% or higher
\citep{Pober:2012p8800}, and comprises a large fraction of the 20\% difference between current telescopes \citep{Jacobs:2013p9908}.

@@

In section \ref{sec:background} we provide some background on uncertainty in early EoR-band catalogs,
and explain our choice of calibrator. Section \ref{sec:approach} gives an overview 
of our approach to making the measurement and motivates our data processing steps, which 
are described in detail in section \ref{sec:Observations}. In section

In section \ref{sec:approach} we describe our approach for measuring source spectra with
drift-scan observations and deriving an absolute flux scale from catalog data.  
In \S\ref{sec:Observations} we detail the instrumental 
setup, observations and analysis method followed. Sections \ref{sec:mcmc} through
\ref{fig:gain} detail our approach for fitting a global flux scale and spectral models for each source.
We use these fits in section \ref{sec:results} to understand how well PAPER data agree
with previous measurements and conclude in \ref{sec:Conclusion}.

\subsection{The sources and instrument}
EoR measurements in the southern sky have focused on the coldest regions where
galactic foregrounds are minimal. With the majority of possible observing time falling on 
RA=4h,Dec=-30. The brightest and least-resolved calibrator in this region is Pictor A 
(5h19m49.1 -45d46m45.0). Pictor A is a nearby FR-II type radio galaxy 
 similar to Cygnus A.  At $\sim$400Jy Pictor is bright and sufficiently distant from other 
bright sources to make it eminently suitable as both a phase and flux calibrator. Its apparent
size of $\sim$8\arcmin{} is smaller than the scales being probed by current EoR instruments , 
making resolution effects, making it suitable for precision calibration.  However, 
like most other sources, precise flux measurements in the EoR band are not available.
The current best EoR band measurement
is uncertain to 12\% and appears to imply spectral flattening in the EoR band
\citep{Perley:1997p9312}.

@@

Establishing an accurate spectrum for Pictor A is of particular importance for
PAPER --- a dedicated EoR experiment 
that employs drift-scanning, dual-polarization dipole antennas 
tuned for efficient operation over a 120--170-MHz band.  PAPER is located in the South African Karoo desert
on the Square Kilometer Array
South Africa (SKA-SA) reserve, 100km north of the small town of Carnarvon.
The PAPER array has grown from 16 elements deployed in early 2009 to a
64-element imaging array in 2011 (see Figure \ref{fig:antpos}). 
Since November 2011 it has been arranged in a maximally redundant grid 
configuration to make deep power spectral integrations \citep{Parsons:2012p9028}.
Though highly sensitive as a power spectrum instrument, the maximally redundant array 
has a broad point spread function in the image domain. This severely limits the number 
of sources which may be used for flux calibration. Drift scanning across the sky with a 45\arcdeg{} FWHM
primary beam there are very few unresolved, bright sources which are far from the galactic plane. 
Pictor A is bright and well enough separated from other emission to dominate the visibilities for a good fraction of
the EoR observing season, making it an ideal flux calibrator.

@@

The response of the primary beam is of critical importance to EoR measurements.
Differences between the polarization responses cause leakage of polarized
signals into the total intensity measurement possibly corrupting the 
EoR power spectrum \citep{Moore:2013p9621}.  The primary beam 
shape is also critical to measuring and subtracting foregrounds 
\cite{Bernardi:2012p9020,Sullivan:2012p9457,Morales:2012p8790} a process which, to be affective, must be done to better than 1\%
precision for the brightest sources \citet{Liu:2009p4762,Bowman:2009p7816} .

A method for decoupling uncertain fluxes from the uncertain beam has been
described by \citet{Pober:2012p8800}. In simulation the method was able to
achieve 3 to 10\% accuracy in measuring the primary beam, depending on the
number of antennae and other variables. The Pober method emphasized the need
for many repeated measurements of each alt-az pointing. Further investigation
is under way to improve and implement this method and would be greatly aided by
the availability of precise flux measurements unaffected by primary beam
uncertainty.

In this paper we provide a set of detailed total flux measurements aimed at providing
an absolute flux calibration for southern hemisphere EoR studies as well as a
small set of verification fluxes suitable for constraining future primary beam studies.

@@

\begin{figure*}
\includegraphics[width=\textwidth]{plots/psa64_pic_strip_positions_psa747_v2_annotated_cropped.png}
\caption{
A PAPER map of the radio sky centered on the south pole showing relative positions of targeted sources. The map was made using the July half of the
data used in this catalog using the procedure described in \citet{Jacobs:2011p8438} to produce a lightly CLEANed map. The circular artifact around the south Celestial pole is due to residual instrumental cross-talk and appears to be highly localized below declinations of 75\arcdeg{} where PAPER's sensitivity is small.  x's mark measured source locations and have size
scaled by dis-agreement with prior data (inverse ``improvement index" from 
\S\ref{sec:results}). Smaller indicates better agreement with past data.  Orange dots indicate sources with no model overlap at 76\% \ref{fig:SI_contour_new}. 
\label{fig:error_map}
}
\end{figure*}
%
%
%
%This model will be effective over a range of declinations, but will diverge at
%some rate depending on the accuracy with which the model describes the slope.  As an estimate of the extrapolated 
%beam amplitude we fit the slope of our Pictor A source track and compute the amplitude extrapolated over our fiducial
%stripe width of 5\arcdeg.
%
%\[
%B = dB/dt dt/\theta \Delta \theta
%\]
%
%Comparing this with the simulation in Figure \ref{fig:beam_extrapolation}, we find that the model predicts the 5\arcdeg{} extrapolation to better
%than 2\% even into the more uncertain areas far from zenith. The RMS difference for the central 15\arcdeg{} of the track
%is 1.5\%. From this we conclude that, as long as we constrain our extrapolations to $\pm5$\arcdeg{} around Pictor A,
%we will have negligible beam area. 
%
%\begin{figure*}
%\includegraphics[width=.9\textwidth]{plots/beam_slope_compare.png}
%\caption{The beam is well along a declination cut but beam formed source tracks. Here we measure the beam, 
%as extrapolated by fitting a slope (dotted), and compare with the beam model (solid). The difference (circles) is never larger
%than $\sim$1\%.  Thus we conclude that the beam slope is locally well modeled and our beam model is suitable 
%for extrapolation over $\sim$5\arcdeg{} scales.
%  \label{fig:beam_extrapolation}}
%\end{figure*}

@@

\subsection*{Data Processing Overview}
\label{sec:data_overview}
The spectra reported here are measured by beam-forming ---phasing the visibilities to
the target location and summing to produce a spectral time series of perceived flux $S_p$. The spectrum is then isolated
from neighboring sources by filtering and averaged in the time domain.  This time average is 
weighted by a model of PAPER's primary beam response ($B$).  
\begin{align}
S_\textrm{est} &= \frac{\sum_t B_M S_p}{\sum_t B^2_M} \nonumber \\ 
&= \frac{\sum_t B_M B}{\sum_t B^2_M} S  \nonumber \\
&= g(\delta) S  \label{eq:g}
\end{align}

As the perceived flux is already weighted once by the true beam $B$ this weighted sum is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800}.

The pre factor in Eq \ref{eq:g} has been integrated in time over the full azimuthal sweep across the sky and therefor depends only on declination. The rate at which this factor
changes with declination defines maximum declination distance we can observe from our calibrator. 
In simulation we multiplied an early holographic beam map \cite{Pober:2012p8800}
by electromagnetic simulations and find that it 
diverges slowly with declination, with a maximum of 10\% over 5\arcdeg{} of declination range, though most are less. 
We estimate this spectral dependent gain at a reference declination of 41\arcdeg{}36\arcmin{}   using (J2331-416) fitting a spectral index model to the
 catalog data points below 2GHz.

@@

At this point we have a set of spectra that have been calibrated relative to each other to the best of our ability. Now 
they must be put on a global flux scale. Meanwhile, our error estimate does not include an estimate of the 
flux calibration error.  To address both points we fit for a global flux scale that incorporates the best available
catalog data. These catalogs
have all been set, as best as possible, to the Baars et al scale to which all other points are tied \citep{Baars:1977p9678}. Using a Bayesian analysis we compute the 
variation in the flux scale implied by comparing many sources to prior catalog models. By including sources from across
the RA/Dec range, the variation in this flux scale fit estimates the overall uncertainty in flux resulting from primary beam 
or prior catalog uncertainty.  This folds in the error due to extrapolation beyond the frequency range of the Baars scale which is
technically limited to 300MHz and above.

@@

Small gain variations between antennae and over time introduce significant systematic effects which degrade 
instrument performance. Temporal variations are dominated by changes in ambient temperature. 
Measurements of ambient temperature versus time on the balun amplifier of a fiducial antenna and near
receiver amplifiers were used to divide out the predicted gain variation versus temperature that these amplifiers
are known to exhibit.  Inspecting the auto correlations we find that the net antenna temperature gain coefficient (-0.042 dB/C) found in previous laboratory \citep{Parashare:2011p9872} and early field 
measurements  \citep{Pober:2012p8800} did not appear to remove all temperature variation.  To
revise the temperature coefficient we use the October observations, when the temperatures remained nearly constant, as a reference.

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{plots/auto_tempcorr.png}
\caption{Calibrating the temperature coefficient  between the July and October observing runs.  Here we plot the ratio of auto-correlations (averaged over frequency and antenna) against the temperature difference between the two nights. The very linear middle region has a slope of  -0.055 dB/C while the full, more complex, range is fit by -0.06dB/C (black line).  We compromise by choosing -0.058dB/C   
which was found to significantly improve the agreement (see Figure \ref{fig:auto_compare}).
\label{fig:autos_tempcorr}}
\end{figure}

\begin{figure}
\includegraphics[width=0.9\textwidth]{plots/auto_balance.png}
\caption{Gain differences between the July and October nights are dominated by temperature variation. Here we see the affect on 
the average auto correlation before ({\color{orange} orange}) and after (black) application of the temperature dependent gain. \label{fig:auto_compare}}
\end{figure}

Matching of relative gains and phases between antenna was done by fitting a per-antenna complex gain to portions
of data which have easily modeled sky. 
This calibration is only relative between antennae, bandpass and absolute flux calibration
comes after time and frequency averaging in sections \ref{sec:Calibration} \ref{sec:flux_scale}.   
The antenna delays and amplitudes were found by fitting a point source visibility
model to Centaurus A, Pictor A, and Fornax A.  Each source is imperfectly
modeled by a single point-source, but the solution differences are minimized by
averaging over the three independent solutions. These same calibration
solutions have been successfully applied in \citet{Pober:2013p9567} and \citet{Stefan:2012p9707}.
for power-spectrum analysis of foregrounds and imaging of Centaurus A, respectively.

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{plots/srcfig_1.png}
\end{center}
\caption{
PAPER spectra of 31 sources compared against existing data out of
\cite{Vollmer:2010p6422} between 40MHz and 2GHz and a sampling
of spectra fits drawn from MCMC samples at greater than 76\% confidence. Sources used to bootstrap the
flux calibration are noted with a * and are shown with the additional calibration data
found in NED. Pictor A is shown separately in Figure \ref{fig:pic_spectrum}.
\label{fig:srcs1}}
\end{figure*}

@@

>>>>

%\title{The Reionization flux scale in the Southern Sky}
\title{A Flux Scale for Southern Hemisphere 21cm EoR Experiments}
\author{
Daniel C. Jacobs\altaffilmark{1},
Aaron R. Parsons\altaffilmark{2,8},
James E. Aguirre\altaffilmark{3},
Zaki Ali\altaffilmark{2},
Judd Bowman\altaffilmark{1},
Richard F. Bradley\altaffilmark{4,5,6},
Chris L.  Carilli\altaffilmark{7},
David R. DeBoer\altaffilmark{8},
Matthew R. Dexter\altaffilmark{8},
Nicole E. Gugliucci\altaffilmark{5},
Pat Klima\altaffilmark{5},
Dave H. E. MacMahon\altaffilmark{8}
Jason R. Manley\altaffilmark{9},
David F. Moore\altaffilmark{3},
Jonathan C. Pober\altaffilmark{2},
Irina I. Stefan\altaffilmark{10},
William P. Walbrugh\altaffilmark{9}}

@@

\begin{abstract}
We present a catalog of spectral measurements covering a 100--200-MHz band for 32 sources, derived
from observations with 
a 64-antenna deployment of the 
Donald C. Backer Precision Array for Probing
the Epoch of Reionization (PAPER) in South Africa.
% ARP: don't think obs dates matter for abstract, observed in July and September of 2011.
For transit telescopes such as PAPER, calibration of the primary beam is
a difficult endeavor, and errors in this calibration are a major source of error in
the determination of source spectra.
In order to decrease reliance on accurate beam calibration,
we focus on calibrating sources in a narrow declination range
from -46\arcdeg{} to -40\arcdeg{}.
Since sources at similar declinations follow nearly identical paths through the primary beam, this
restriction greatly reduces errors associated with beam calibration,
yielding a dramatic improvement in the accuracy of derived source spectra.
Extrapolating from higher frequency
catalogs, we derive the flux scale using a Monte-Carlo fit across multiple sources that 
includes uncertainty from both catalog and measurement errors. Fitting spectral 
models to catalog data and these new PAPER measurements, we derive new flux models for
Pictor A and \Nconf{} other sources as nearby declinations, 
90\% are found to confirm and refine a power-law model for flux density.
Of particular importance is the new Pictor A flux model, which is accurate to
1.4\% and shows, in contrast to previous models, that between 100 MHz and 2 GHz, the spectrum of Pictor A 
is consistent with a single power law given by a flux at 150 MHz of
381.9$\pm$5.4 Jy, and a spectral index of -0.76$\pm$0.01.  
This accuracy represents 
an order of magnitude improvement over previous measurements in this band, and
is limited by the uncertainty in the catalog measurements used
to estimate the absolute flux scale.  The simplicity and improved accuracy of Pictor A's spectrum
make it an excellent calibrator in a band of
importance to experiments seeking to
measure 21cm emission from the Epoch of Reionization. 
\end{abstract}

@@

Numerous radio telescopes are now exploring the prospects for using
measurements of highly redshifted 21cm emission to inform our understanding of
cosmic reionization in the redshift range $z>6$, corresponding to radio
frequencies below 200 MHz (see reviews in
\citealt{Furlanetto:2006p2267,Morales:2010p8093,Pritchard:2012p9555}).  These
include telescopes aiming to measure the global temperature change of 21cm
emission during the Epoch of Reionization (EoR), such as the Compact
Reionization Experiment (CoRE), the Zero-spacing Interferometer \citep{Raghunathan:2011}  and the Experiment to Detect the Global EoR
Signature (EDGES; \citealt{Bowman:2010p8546}), and interferometers aiming to
measure the power spectrum of 21cm EoR emission, such as the Giant Metre-wave
Radio Telescope (GMRT;
\citealt{Paciga:2011p9470,Paciga:2013p9627})\footnote{\url{http://gmrt.ncra.tifr.res.in/}},
the LOw Frequency ARray (LOFAR;
\citealt{Yatawatta:2013p9699})\footnote{\url{http://www.lofar.org/}}, the
Murchison Widefield Array (MWA;  \citealt{Bowman:2012p9138};
\citealt{Tingay:2013p9022}))\footnote{\url{http://www.mwatelescope.org/}}, and
the Donald C. Backer Precision Array for Probing the Epoch of Reionization
(PAPER; \citealt{Parsons:2010p6757,Pober:2013p9567})\footnote{\url{http://eor.berkeley.edu/}}.

As such, there has been a renewed interest in the spectral and spatial variation of
foreground emission in the 100--200 MHz frequency band that covers
the $z=6$--13 redshift range expected to encompass reionization
\citep{Furlanetto:2006p2267}. % XXX I think this sentence is a repeat from another paper
In particular, the spectral properties of extra-galactic point-sources are important
both because they are valuable calibration references
and because they are strong foreground emitters that must be removed from 21cm EoR measurements.
With the sparse availability of measured foreground properties in the
100--200-MHz frequency band over large areas of the sky \citep{deOliveiraCosta:2008p2242}, continued
foreground characterization is a
vital step en route to any 21cm EoR detection.
At these low
frequencies, the Southern sky is much less well known than the North;
catalog source fluxes at 150MHz are inaccurate at the 20\% level
for $\delta<-20$\arcdeg{} \citep{Slee:1995p7541,Vollmer:2005p6425}.
Both PAPER and the MWA are located in the southern hemisphere at radio-quiet
reserves being prepared for the upcoming Square Kilometer Array, and hence,
the
most extensive surveying work is now being conducted by the EoR experiments
themselves \citep{Jacobs:2011p8438,Williams:2012p8768,Bernardi:2013p9859}.

One significant complication to improving the state of affairs in foreground characterization
is that many 21cm EoR experiments, including LOFAR in the northern hemisphere, and
PAPER and MWA in the southern hemisphere, are designed for drift-scan observations or steered via phased array.
This design decision has largely been driven by the simplicity and cost-effectiveness of
phased and/or correlated dipoles to achieve the aggressive sensitivity requirements
for measuring the 21cm power spectrum of reionization.
%TODO ARP wanted a cite for the above.  I really don't know of a good one. Its it a bit of a broad statement
% XXX how about Parsons 2012a, Beardsley 2012, and jelic 2008 (i think it has sensitivty for lofar)
Adding to the challenge, these telescopes 
cover much wider fields of view ($>10$\arcdeg) and bandwidths
($\sim 100$\% fractional) than traditional dish telescopes.
Because they do not physically point, flux calibration for such arrays relies heavily
on an accurate model of the primary beam response to correct for an
the apparent flux scale that varies across the sky.
This direction dependent gain is currently uncertain to 10\% or higher
\citep{Pober:2012p8800}, and comprises a large fraction of the 20\% difference between current telescopes \citep{Jacobs:2013p9908}.
% XXX difference of what?

@@

In \S\ref{sec:background} we provide some background on uncertainty in early EoR-band catalogs,
and explain our choice of calibrators.
In \S\ref{sec:approach} we describe our approach for measuring source spectra with
drift-scan observations and deriving an absolute flux scale from catalog data.  
In \S\ref{sec:Observations} we detail the instrumental 
setup, observations and analysis method followed. Sections \ref{sec:mcmc} through
\ref{fig:gain} detail our approach for fitting a global flux scale and spectral models for each source.
We use these fits in \S\ref{sec:results} to understand how well PAPER data agree
with previous measurements and conclude in \S\ref{sec:Conclusion}.

\subsection{The sources and instrument}
EoR measurements in the southern sky have focused on the coldest regions where
galactic foregrounds are minimal. With the majority of possible observing time falling around
RA=4h,Dec=-30. The brightest and least-resolved calibrator in this region is Pictor A 
(5h19m49.1,-45d46m45.0). Pictor A is a nearby FR-II type radio galaxy 
 similar to Cygnus A.  At $\sim$400Jy, Pictor is bright and sufficiently distant from other 
bright sources to make it eminently suitable as both a phase and flux calibrator. Its apparent
size of $\sim$8\arcmin{} is smaller than the scales being probed by current EoR instruments, 
making it suitable for precision calibration, with only a modest
level of resolution effects.
However, 
like most other sources, precise flux measurements in the EoR band are not available.
The previous best EoR band measurement
is uncertain to 12\% and appears to imply spectral flattening in the EoR band
\citep{Perley:1997p9312}.

@@

Establishing an accurate spectrum for Pictor A is of particular importance for
PAPER --- a dedicated EoR experiment 
that employs drift-scanning, dual-polarization dipole antennas 
tuned for efficient operation over a 120--170-MHz band.  PAPER is located in the South African Karoo desert
on the Square Kilometer Array
South Africa (SKA-SA) reserve, 100km north of the small town of Carnarvon.
The PAPER array has grown from 16 elements deployed in early 2009 to a
64-element imaging array in 2011 (see Figure \ref{fig:antpos}). 
Since November 2011 it has been arranged in a maximally redundant grid 
configuration to make deep power spectral integrations \citep{Parsons:2012p9028}.
Though highly sensitive as a power spectrum instrument, the maximally redundant array 
has a broad point spread function in the image domain. This severely limits the number 
of sources which may be used for flux calibration. Drift scanning across the sky with a 45\arcdeg{} FWHM
primary beam, there are very few unresolved, bright sources which are far from the galactic plane. 
Pictor A is bright and well enough separated from other emission to dominate the visibilities for a good fraction of
the EoR observing season, making it an excellent flux calibrator.

@@

The response of the primary beam is of critical importance to EoR measurements.
Differences between the polarization responses cause leakage of polarized
signals into the total intensity measurement possibly corrupting the 
EoR power spectrum \citep{Moore:2013p9621}.  The primary beam 
shape is also critical to measuring and subtracting foregrounds 
\cite{Bernardi:2012p9020,Sullivan:2012p9457,Morales:2012p8790} a process which, to be effective, must be done to better than 1\%
precision for the brightest sources \citet{Liu:2009p4762,Bowman:2009p7816} .

A method for decoupling uncertain fluxes from the uncertain beam has been
described by \citet{Pober:2012p8800}. In simulation the method was able to
achieve 3 to 10\% accuracy in measuring the primary beam, depending on the
number of antennae and other variables. The Pober method emphasized the need
% XXX mention key assumption of 180deg rotational symmetry
for many repeated measurements of each alt-az pointing. Further investigation
is under way to improve and implement this method and would be greatly aided by
the availability of precise flux measurements unaffected by primary beam
uncertainty.

In this paper we provide a set of detailed total flux measurements aimed at providing
an absolute flux calibration for southern hemisphere EoR studies, as well as a
small set of verification fluxes suitable for constraining future primary beam studies.

@@

\begin{figure*}
\includegraphics[width=\textwidth]{plots/psa64_pic_strip_positions_psa747_v2_annotated_cropped.png}
\caption{
A PAPER map of the radio sky centered on the south pole showing relative positions of targeted sources. The map was made using the July half of the
data used in this catalog using the procedure described in \citet{Jacobs:2011p8438} to produce a lightly CLEANed map. The circular artifact around the south Celestial pole is due to residual instrumental cross-talk and appears to be highly localized below declinations of 75\arcdeg{} where PAPER's sensitivity is small.  `x''s mark measured source locations and have size
scaled by disagreement with prior data (inverse ``improvement index" from 
\S\ref{sec:results}). Smaller indicates better agreement with past data.  Orange dots indicate sources with no model overlap at 76\% in Figure \ref{fig:SI_contour_new}. 
\label{fig:error_map}
}
\end{figure*}
%
%
%
%This model will be effective over a range of declinations, but will diverge at
%some rate depending on the accuracy with which the model describes the slope.  As an estimate of the extrapolated 
%beam amplitude we fit the slope of our Pictor A source track and compute the amplitude extrapolated over our fiducial
%stripe width of 5\arcdeg.
%
%\[
%B = dB/dt dt/\theta \Delta \theta
%\]
%
%Comparing this with the simulation in Figure \ref{fig:beam_extrapolation}, we find that the model predicts the 5\arcdeg{} extrapolation to better
%than 2\% even into the more uncertain areas far from zenith. The RMS difference for the central 15\arcdeg{} of the track
%is 1.5\%. From this we conclude that, as long as we constrain our extrapolations to $\pm5$\arcdeg{} around Pictor A,
%we will have negligible beam area. 
%
%\begin{figure*}
%\includegraphics[width=.9\textwidth]{plots/beam_slope_compare.png}
%\caption{The beam is well along a declination cut but beam formed source tracks. Here we measure the beam, 
%as extrapolated by fitting a slope (dotted), and compare with the beam model (solid). The difference (circles) is never larger
%than $\sim$1\%.  Thus we conclude that the beam slope is locally well modeled and our beam model is suitable 
%for extrapolation over $\sim$5\arcdeg{} scales.
%  \label{fig:beam_extrapolation}}
%\end{figure*}

@@

\subsection*{Data Processing Overview}
\label{sec:data_overview}
The spectra reported here are measured by beam-forming ---phasing the visibilities to
the target location and summing over baselines to produce a spectral time series of perceived flux $S_p$,
which is given by the true source flux, $S$, illuminated by the true beam pattern $B$, according to
% XXX would be nice to capture here and below that B, B_M, and S_p are vectors indexed by t.  would
% suggest subscript, except you already have B_M.  Could use B^\prime (and S^\prime) instead...
\begin{equation}
S_p=BS.
\end{equation}
The spectrum is then isolated
from neighboring sources by filtering and averaged in the time domain.  This time-average is 
weighted by a model of PAPER's primary beam response ($B_M$).  
\begin{align}
S_\textrm{est} &= \frac{\sum_t B_M S_p}{\sum_t B^2_M} \nonumber \\ 
&= \frac{\sum_t B_M B}{\sum_t B^2_M} S  \nonumber \\
&= g(\delta) S  \label{eq:g}
\end{align}
% XXX where g and \delta are...?  Should connect this nomeclature to J2331-416 language below (i.e. solving for g)
As the perceived flux is already weighted once by the true beam $B$ this weighted sum is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800}.

The pre-factor in Eq \ref{eq:g} has been integrated in time over the full azimuthal sweep across the sky and therefore depends only on declination. The rate at which this factor
changes with declination defines maximum declination distance we can observe from our calibrator. 
In simulation we multiplied an early holographic beam map \cite{Pober:2012p8800}
% XXX to simulate what?  need to say something like:
% To simulate the effect of beam model errors on ???, we used simulations derived from the holographic
% beam map measured in \citet{Pober:2012p8800} weighted by a beam model derived from electromagnetic
% simulations, and find that ...
by electromagnetic simulations and find that it 
diverges slowly with declination, with a maximum of 10\% over 5\arcdeg{} of declination range, though most are less. 
We estimate this spectral dependent gain at a reference declination of 41\arcdeg{}36\arcmin{}   using (J2331-416) fitting a spectral index model to the
 catalog data points below 2GHz. 
% XXX clarify that this is not the last correction; there is one more flux cal that is derived from MCMC
% over several calibrator sources (Figure XXX).

@@

At this point we have a set of spectra that have been calibrated relative to each other to the best of our ability. Now 
they must be put on a global flux scale. Meanwhile, our error estimate does not include an estimate of the 
flux calibration error.  To address both points we fit for a global flux scale that incorporates the best available
catalog data. These catalogs
have all been set, as best as possible, to the \citet{Baars:1977p9678} scale to which all other points are tied. Using a Bayesian analysis we compute the 
variation in the flux scale implied by comparing many sources to prior catalog models. By including sources from across
the RA/Dec range, the variation in this flux scale fit estimates the overall uncertainty in flux resulting from primary beam 
or prior catalog uncertainty.  This folds in the error due to extrapolation beyond the frequency range of the Baars scale which is
technically limited to 300MHz and above.

@@

Small time- and antenna-dependent gain variations time introduce significant systematic effects that degrade 
instrument performance. Temporal variations are dominated by changes in ambient temperature. 
We use measurements of ambient temperature versus time on the balun amplifier of a fiducial antenna and near
receiver amplifiers to divide out the predicted gain variation versus temperature that these amplifiers
are known to exhibit.  Inspecting the auto correlations we find that the net antenna temperature gain coefficient (-0.042 dB/C) found in previous laboratory \citep{Parashare:2011p9872} and early field 
measurements  \citep{Pober:2012p8800} did not appear to remove all temperature variation.  To
revise the temperature coefficient we use the October observations, when the temperatures remained nearly constant, as a reference.

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{plots/auto_tempcorr.png}
\caption{Calibrating the temperature coefficient  between the July and October observing runs.  Here we plot the ratio of auto-correlations (averaged over frequency and antenna) against the temperature difference between the two nights. The very linear middle region has a slope of  -0.055 dB/C while the full, more complex, range is fit by -0.06dB/C (black line).  We compromise by choosing -0.058dB/C   
which was found to significantly improve the agreement (see Figure \ref{fig:auto_compare}).
% XXX When comparing autos from different JDs, the change in position of sun can substantially affect signal level
% I'm worried this is the cause of the dither on either end of Figure 3, unless you've been conservative about
% what data you've included here.
\label{fig:autos_tempcorr}}
\end{figure}

\begin{figure}
\includegraphics[width=0.9\textwidth]{plots/auto_balance.png}
\caption{Gain differences between the July and October nights are dominated by temperature variation. Here we see the affect on 
the average auto correlation before ({\color{orange} orange}) and after (black) application of the temperature dependent gain. \label{fig:auto_compare}}
% XXX why does the gap in data in the top plot not match the bottom?
\end{figure}

Matching of relative gains and phases between antenna was done by fitting a per-antenna complex gain to portions
of data which have easily modeled sky. 
This calibration is only relative between antennae, bandpass and absolute flux calibration
comes after time and frequency averaging in sections \ref{sec:Calibration} and \ref{sec:flux_scale}.   
The antenna delays and amplitudes were found by fitting a point source visibility
model to Centaurus A, Pictor A, and Fornax A.  Each source is imperfectly
modeled by a single point-source, but the solution differences are minimized by
averaging over the three independent solutions. These same calibration
solutions have been successfully applied in \citet{Pober:2013p9567} and \citet{Stefan:2012p9707}.
for power-spectrum analysis of foregrounds and imaging of Centaurus A, respectively.

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{plots/srcfig_1.png}
\end{center}
\caption{
PAPER spectra of 31 sources compared against existing data out of
\cite{Vollmer:2010p6422} between 40MHz and 2GHz and a sampling
of spectra fits drawn from MCMC samples at greater than 76\% confidence. Sources used to bootstrap the
flux calibration are noted with a `*' and are shown with the additional calibration data
found in NED. Pictor A is shown separately in Figure \ref{fig:pic_spectrum}.
\label{fig:srcs1}}
\end{figure*}

@@

% XXX re-check arxiv cites in bib for finishing peer review.  Paciga 2013, Pober 2013, Moore 2013, and Stefan 2013
% all published now.  what is bernardi 2012 submitted?
